Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-08 manuscript/supplements_rsfmri.Rmd
reverted deletion of Fraukes changes in draft_rsfmri.Rmd

```{r DMN_BMI_splitFD results, caption="Model 2c for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R1), custom.coef.names=c("Intercept", "average BMI", "change BMI", "average mFD", "change mFD", "Age", "Sex"), custom.model.names = "R1", float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
\newpage
```{r, include = FALSE}
library(dplyr)
DIR_ANALYSIS <- "/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis"
df <- file.path(DIR_ANALYSIS,"noExclFD/result_report.txt")
AnatomyResults <- read.table(df, sep="\t",col.names = c("model","dir","k"),stringsAsFactors = FALSE)

txtList <- list()

for (r in 1:nrow(AnatomyResults)) {

  file = AnatomyResults[r,"dir"]
  txt_cols <- c("VoxelCount","equals","PercClusterVolumeAssignedTo","in","Hem","Region","PercentOfArea","V8","V9","V10","V11","V12","V13")
  txt <- read.table(trimws(f),sep="\t",fill=TRUE,col.names=txt_cols) # paste0("V", 1:13)

  txt <- txt[sort(c(which(grepl("Cluster", txt$VoxelCount)),which(grepl("voxel", txt$equals)))),]
  txt <- txt[,c("VoxelCount","PercClusterVolumeAssignedTo", "Hem","Region","PercentOfArea")]

  idxClusterStart <- which(grepl("Cluster", txt$VoxelCount))

  #txt$VoxelCount <- as.character(txt$VoxelCount)
  txt <- cbind(descr = NA, txt)
  txt$descr[idxClusterStart] <- stringr::str_remove(string = as.character(txt$VoxelCount[idxClusterStart]), pattern = "\\:[^:]*$")
  txt$VoxelCount[idxClusterStart] <- NA

  # attach model with  cluster list to list of models
  name_model <- AnatomyResults$model[r]
  txtList[[name_model]] <- txt
}

txt_colname <- kableExtra::linebreak(c("Cluster","Number of voxels\n in cluster","\\% of cluster volume\nassigned", "Hemisphere","Area","\\% of area overlap\nwith cluster"))

TableList <- list()
for (i in 1:length(txtList)){
  TableList[[i]] <-
    txtList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = txt_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = sprintf("Anatomical labelling for %s",name_model[i]),
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
}
```

@@

```{r, echo=FALSE}

AnatomyResults$model <- read.table(df, sep="\t",col.names = c("model","dir","k"),stringsAsFactors = FALSE)[1]
l <- stringr:: str_split(AnatomyResults$model, '_')
d <- data.frame(matrix(unlist(l), nrow=length(l), byrow=T))
#stringr::str_replace(as.character(d[,2]),"^\\(PCC|NACC)cc$"," (cc)") # , "\\(PCC|NACC)(gsr)" = "(gsr)"

TableList[[1]]
TableList[[2]]
TableList[[3]]
TableList[[4]]
TableList[[5]]
TableList[[6]]
TableList[[7]]
TableList[[8]]
TableList[[9]]
```

>>>>

```{r DMN_BMI_splitFD results, caption="Model 2c for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R1), custom.coef.names=c("Intercept", "average BMI", "change BMI", "average mFD", "change mFD", "Age", "Sex"), custom.model.names = "R1", float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
\newpage
```{r, include = FALSE}

source("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/code/tables.R")

ToolboxOutputList <- mk_DetailedLabelTab()
TableList_colname <- kableExtra::linebreak(c("Cluster","Number of voxels\n in cluster","\\% of cluster volume\nassigned", "Hemisphere","Area","\\% of area overlap\nwith cluster"))

TableList <- list()
for (i in 1:length(ToolboxOutputList$EntryList)){
  TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
}
```

@@

```{r, echo=FALSE}
TableList[[1]]
TableList[[2]]
TableList[[3]]
TableList[[4]]
TableList[[5]]
TableList[[6]]
TableList[[7]]
TableList[[8]]
TableList[[9]]
```
